
\section{Experimental Protocol}\label{sec:experimental-protocol}
In this section, we will describe how our experiments are run and what we want to measure.
We also discuss which parameters we can adjust in the various experiments we have.

The experiments are run on a virtual machine hosted on Strato CLAAUDIA at Aalborg University.
It features 16 virtual CPUs (VCPUs) and 64 GB of RAM\@.
Those VCPUs are based on an Intel Xeon Gold 6254 CPU with a 3.10 GHz clock speed.
One VCPU does not correspond to one physical CPU but rather to a hardware thread within the used CPU\@.
Additionally, the VCPUs are over-provisioned, which means that the computation time may be shared with other virtual machines on the same server\footnote{\text{As explained in an earlier documentation of Strato: }\\ \href{https://github.com/aau-claaudia/Documentation/blob/0d40577ed757c5e9640109f5aac5a7f0a36b7f85/docs/guides/performance/performance.md}{https://github.com/aau-claaudia/Documentation/blob/\\0d40577ed757c5e9640109f5aac5a7f0a36b7f85/docs/guides/\\performance/performance.md}. Accessed: 10/06/2025}.
The virtual machine is running Ubuntu Server 24.


\subsection{CAAUrdleproof}\label{sec:CAAUrdleproof-experiment}
In this experiment, we measure the time to run the CAAUrdleproofs protocol.
The results will be compared to those of Curdleproofs, which we re-run on our hardware.
As Curdleproofs already has a Rust benchmark implemented, we will be using that same benchmark for both protocols.
The parameter that we want to change between benchmark runs is the shuffle size, $\ell$.

In CAAUrdleproofs, we will test the protocol with $\ell=\{8,9,\dots,256\}$.

Since Curdleproofs is unable to run benchmarks, unless the shuffle size is a power of two, those benchmarks will be run on values $\ell=2^N$, where $N=\{3,4,5,6,7,8\}$.




\subsection{Shuffle security}\label{subsec:experimental-protocol-shuffle-security}
In this experiment, we run the shuffle protocol with varying shuffle sizes and varying numbers of adversarial tracked ciphertexts.
The purpose of this experiment is to find the lowest possible shuffle size that is still secure against adversarial tracking.
We, therefore, run the experiment with shuffle sizes,~$\ell$, between 32 and 512.
For the number of adversarial tracked ciphertexts, we use the values $\alpha=\{1/2,1/3,1/4\}$

Because Curdleproofs is meant to be used in an Ethereum setting, a maximum of 8,192 shuffles is available.
However, we will keep running the shuffling experiments until they are deemed secure.
Additionally, the experiments are conducted with a set of 16,384 ciphertexts.
Both of these numbers come from the Ethereum Whisk proposal~\cite{Whisk2024}.
Every experiment is run 1,000 times to avoid statistical uncertainty.