
\section{Attacks on Ethereum}\label{sec:attacks-on-ethereum}
The following section explains different attacks that can or could happen to the Ethereum blockchain.
There is a description of both the attack and its possible mitigation.
If found, there will be a link to a~\gls{poc} of the attack and/or the proposed/implemented mitigation.
\subsection{Reorg}\label{subsec:reorg}
One of the reorganization attacks is \textit{Commitment Attacks on LMD GHOST}~\cite{sarenche2024breakingbalancepowercommitment}.
It works by using financial incentives to convince validators to vote for a prior block in the chain, saying they will be committing to it, to try and exploit their laziness.
This attack is possible because around 90\% of validators use software called "MEV Boost" which tries to earn you the most money and is unwilling to risk not getting a reward.

Another reorg attack is Short-range reorg, which uses short-range reorgs of the blockchain stipulating consensus to delay the finality of consensus decisions~\cite{10.1007/978-3-031-18283-9_28}.
Such short-range reorgs also allow validators to increase their earnings from participating in the protocol.
It does this by withholding a block and releasing it when the next honest block is proposed to orphan it.
This attack requires a large amount of stake to be held by the adversary, with 30\% being the aim and everything below only reducing the chance of success.

A reorg attack inspired by the last attack is a Low-cost, long-range reorg attack\cite{10.1007/978-3-031-18283-9_28}.
This attack works by the adversary, avoiding competing directly with honest validators of $(k-1)$ committees, as in the short-range reorg attack.
Instead, the adversary uses the technique of balancing attacks to keep honest committee members roughly split in half by ensuring they have different views on the current head of the chain.
This split in the perception of the honest chain makes honest nodes work against each other to maintain a tie that the adversary can tip to their liking at any point using only a few votes.
A possible mitigation is the recently proposed Transaction Encapsulation approach, which demonstrates that some cross-layer attacks can be alleviated or prevented by dynamic transactions ~.

A different reorg attack is called $>=50\%$ stake attack~\cite{EthereumAttackDefense2024}.
The attack works if the adversary has more than 50\% of the staked ether.
The adversary would be able to have the majority vote every time in the fork choice algorithm.
This would mean that all honest validators must vote with the adversary to prevent their ether from being burned due to the inactivity leak security protocol.
Because of said protocol, the adversary would also eventually gain finalization.
This attack also allows the adversary to easily reorg a block.
Given the significant stake needed for the attack to work, this attack would not be feasible on most blockchain systems.



\subsection{DoS}\label{subsec:dos}
We have found two other kinds of~\gls{dos} attacks that were or could be performed on Ethereum.

One of the attacks is called \textit{under-priced opcodes}~\cite{10.1145/3391195,9815256}.
This attack works because Ethereum has a gas mechanism to reduce the abuse of computing resources.
However, when a contract has a lot of underpriced opcodes, it will consume many resources.
Execution of contracts requires many resources.

To mitigate this,
Ethereum has raised the gas cost of opcodes
to preserve the number of transactions-per-second~\cite{Opcode-mitigation}~\footnote{
    \href{https://github.com/ethereum/EIPs/blob/master/EIPS/eip-150.md}{EIPs/EIPS/eip-150.md at master ethereum/EIPs GitHub}}.

Another attack, which is closely related to the former, is \textit{empty account in the state trie}~\cite{10.1145/3391195,9815256}.
This attack was possible because the existence of empty accounts increases the transaction processing time and synchronization.
An empty account is an account with zero balance and no code.
The attack required the proposer to select only the adversary's transactions, which could be insured by offering a higher gas price.

The mitigation is a combination of the one explained for \textit{under-priced opcodes} as well as a mitigation
for clearing empty accounts~\cite{Opcode-mitigation,empty-account-mitigation,empty-account-eip-mitigation}~\footnote{
    \href{https://github.com/ethereum/EIPs/blob/master/EIPS/eip-161.md}{EIPs/EIPS/eip-161.md at master ethereum/EIPs GitHub}}.


\subsection{Balancing Attack}\label{subsec:balancing-attack}
For this type, we found two attacks.

The first attack we call \textit{LMD-specific balancing attack}~\cite{10.1145/3560829.3563560}.
This attack exploits the~\gls{lmd} \textit{proposer boosting} by sending out two competing blocks but giving half the validators one block before the other and the opposite for the other half.
This would create a fork in the blockchain, and one of the two branches would be dishonest.

Although no mitigation is mentioned, it requires $W_p/b+1$ adversarial slots~\footnote{where $W_p$ is the proposer boost weight (fx 100 validators/slot: $W_p=0.7\cdot100=70$) and $b$ is the fraction of adversaries in the committee in each slot}.


Another balancing attack has the adversary exploiting adversarial network delay and strategic voting by a vanishing fraction of adversarial validators to stall the protocol indefinitely~\cite{10.1007/978-3-031-18283-9_28}~\footnote{\href{https://github.com/tse-group/gasper-gossip-attack}{GitHub - tse-group/gasper-gossip-attack}}.

This attack does depend on networking assumptions that are highly contrived in practice, such as the attacker having fine-grained control over the latencies of individual validators.

\subsection{Finality Attack (Bouncing Attack)}\label{subsec:finality-attack-(bouncing-attack)}
In Ethereum, there exist finality attacks, also known as bouncing attacks, which deny the blockchain the ability to finalize its block, halting its functionality.

The first attack is a \textit{double finality} attack~\cite{EthereumAttackDefense2024, 10646904}, Where two forks finalize simultaneously, creating a permanent chain split.
It is theoretically possible for an attacker who wants to risk 34\% of the total staked ether.

A way to see a mitigation of this is that it is practically impossible given the current value of 34\% of the total staked ether.
Also, voting on two different chains, called double voting, is a slash-able offense in the Ethereum chain, so the adversary would get their staked ether slashed.


Another finality attack is called \textit{33\% finality attack}~\cite{EthereumAttackDefense2024}.
All adversarial ($\geq33\%$) validators can go inactive,
meaning a block cannot get the $2/3$ attestations required to achieve finality.
Therefore, the blockchain would not be able to go further, as it would not be able to achieve finality.

The mitigation for this is called \textit{the inactivity leak}.
The Ethereum chain penalizes the validators who resist voting or are inactive.
Their ether gets burned until the majority vote has a 2/3 majority.
This mitigation makes the attack impractical for the attacker, as it is costly to have $\geq33\%$ of the total staked ether, and their ether gets burned as well.

\subsection{Avalanche Attack}\label{subsec:avalanche-attack}
This type only includes a single attack that we call \textit{avalanche attack on proof-of-stake ghost}~\cite{10.1145/3560829.3563560}~\footnote{
\href{https://github.com/tse-group/pos-ghost-attack?tab=readme-ov-file}{GitHub - tse-group/pos-ghost-attack}}.
The attack uses withheld blocks to make wide subtrees to displace an honest chain.
It does this by exploiting the reuse of uncle blocks.

The mitigation for this attack is already a part of the Ethereum blockchain~\footnote{\href{https://github.com/ethereum/consensus-specs/pull/2730}{Proposer LMD Score
Boosting by adiasg Pull Request \#2730 ethereum/consensus-specs GitHub}}.
It is mitigated by~\gls{lmd}, which works together with~\gls{ghost}.
The protocol only counts a vote from a validator if the vote is strictly later than the current entry.
If two equivocating votes were sent from the same validator at the same time slot,
only the earlier message would be counted.

\subsection{Bribery}\label{subsec:bribery}
An adversary using bribery attacks on the Ethereum chain could be interested in dictating a choice in some voting mechanism.
In the \textit{quadratic funding} attack~\cite{EthereumAttacks2024}.
The adversary researches votes on the chain and bribes users to vote for what the adversary wants.

In defense of a potential bribery attack, the Ethereum blockchain implements a private voting system called~\gls{maci}~\cite{EthereumAttacks2024,MACI2022}~\footnote{
    \href{https://github.com/privacy-scaling-explorations/maci}{GitHub -
    privacy-scaling-explorations/maci: Minimal Anti-Collusion Infrastructure (MACI)}}.

What~\gls{maci} does is hide what each person has voted for.
It does so by demanding that the voters send their votes encrypted to a central coordinator.
This coordinator constructs~\gls{zk-snark} proofs, which verify that all messages were processed correctly and that the final result corresponds to the sum of all valid votes.

As votes are now hidden, the adversary is not able, by itself, to prove that the bribee voted in the way of said bribery.
The bribee could decrypt their own message and show the vote to the adversary to try to circumvent the mitigation.

~\gls{maci} has fixed this problem by implementing public key switching, meaning a voter can request a new public key.
In addition, a vote is only valid if it uses the voter's most recent public key.
Therefore, a bribee can show that its first vote obeyed the adversary, then generate a new public key and send a new, now honest, vote.
The old vote becomes invalid as it uses a deprecated public key.

\subsection{Staircase Attack}\label{subsec:staircase-attack}
The last type of attack that we cover is called a \textit{staircase attack}.
It is a two-part attack, with a warm-up attack and a full attack~\cite{cryptoeprint:2023/1622}~\footnote{
\href{https://github.com/tsinghua-cel/Staircase-Attack}{GitHub - tsinghua-cel/Staircase-Attack: This is the staircase attack implement for the paper "Max Attestation Matters: Making Honest Parties Lose Their Incentives in Ethereum PoS."}}.

First, we will cover the \textit{warm-up attack}.
The attack works when the adversary, called $a$, has to propose the first block of an epoch.
From there, the attack works in four parts:
\begin{enumerate}
    \item The adversary withholds its block at slot $t$
    \item The honest attestors in slot $t$ create attestation with the last block of the previous epoch, called $b$.
    \item Adversary $a$ releases block $b_t$ and honest validators update their checkpoint to block $b_t$.
    \item Attestations with targets different from $b_t$ will be discarded, and honest attestors in slot $t$ will be penalized eventually
\end{enumerate}

This attack is mitigated by what Ethereum calls \textit{honest reorg}, which should prevent intentionally withheld blocks~\cite{cryptoeprint:2023/1622}.

A block proposed in slot t with fewer than 20\% attestations is considered invalid.
It can be theoretically avoided with network timing, ensuring that at least 20\% of the attestors get the block.


With the \textit{warm-up attack}, the author describes a full \textit{staircase attack}.
The attack starts with the \textit{warm-up attack}.
Then, the plan is to manipulate the source of the honest validators.
Half the validators should get an outdated \textit{last justified checkpoint} and be penalized.
All byzantine validators withhold their blocks and publish them in the middle of the epoch.
It should be able to be done as a one-time attack with a probability of 98.84\% if the adversary controls at least N/3 validators~\cite{cryptoeprint:2023/1622}.
The byzantine validators are not penalized but will get a smaller reward than the fair share.

What would make this attack infeasible is that it would require a lot of controlled validators.
The author states that for Ethereum to be vulnerable, there would need to be $<16,384$ validators, which makes the attack as good as impossible given Ethereum has $~1,073,406$ daily active validators~\cite{cryptoeprint:2023/1622}~\footnote{According to \href{https://beaconcha.in/charts/validators}{beaconcha.in} as of 22-10-2024}.
Also, Ethereum released a patch fixing this attack after the author pointed it out~\footnote{\href{https://github.com/ethereum/consensus-specs/pull/3339\#issuecomment-1637117341}{Confirmation Rule by saltiniroberto Pull Request \#3339 ethereum/consensus-specs GitHub}}.